A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-07-01 tex/paper.tex
new phoenix

\begin{deluxetable}{rr}
\tablecaption{Nomenclature used in this document}
\tablehead{
  \colhead{Symbol} & \colhead{Description}
}
\startdata
%Symbol & Description\\
%\hline
%\hline
$i$ & index specifying a pixel\\
%$\lambda_i$ & wavelength corresponding to a given pixel $i$\\
%$\vg$ & fundamental stellar parameters, $T_{\rm eff}, \log(g), \Z, \A$\\
%  & that parameterize a synthetic spectrum from the grid\\
%$\vpp$ & stellar parameters $v \sin i$, $v_z$, $A_V$, and $R^2/d^2$ that\\
%  & are applied during ``post processing'' of the synthetic spectrum\\
%$\vtstar$ & $\{\vg,\vpp \}$\\
%$\finst(\lambda)$ & data spectrum\\
%$\fsynth(\lambda)$ & synthetic spectrum\\
%$\vtcheb$ & the set of Chebyshev polynomial coefficients $\{c_0, c_1, \ldots, c_N\}$\\
%$\vtline{1}$ & \\
%$\vtlines$ & \\
%$\vtorder{1}$ & \\
%$\vtorders$ & \\
%$\vt$ & the parameters $\{\vg, \vpp, \vN\}$ that completely describe a model spectrum\\
%$\fDi$ & data flux for a given pixel, $D(\lambda_i)$\\
%$\fD$ & data vector comprised of all $\fDi$, $i = \{1, \ldots, N\}$\\
%$\fMi$ & model flux for a given pixel, $M(\lambda_i | \vt)$\\
%$\fM$ & model vector comprised of all $\fMi$, $i = \{1, \ldots, N\}$\\
%$\sigma_i$ & Poisson noise for a given pixel $i$\\
%$R_i$ & residuals $\fDi - \fMi$\\
%$\fR$ & residual vector $\fD - \fM$\\
%$C$ & covariance matrix\\
%$\sigma_{ij}$ & element in the covariance matrix\\
%$r(\lambda_i, \lambda_j)$ & radial distance in wavelength space corresponding to $\Delta v$\\
%$k_{\rm global}$ & global covariance kernel\\
%$k_{\rm line}$ & regional covariance kernel\\
%\hline
%\caption{Nomenclature used in this document.}
%\label{tab:nomenclature}
\enddata
\end{deluxetable}

\begin{deluxetable}{rr} 
\tablecaption{\label{table:tests} Tests}
\tablehead{\colhead{Object} & \colhead{Orders}}
\startdata
WASP-14 & 22-24 \\
WASP-14 & 22-24 \\
WASP-14 & 22-24 \\
WASP-14 & 22-24 \\
\enddata
\end{deluxetable}

>>>>

\begin{deluxetable}{ll}
\tablecaption{Nomenclature used in this document}
\tablehead{
  \colhead{Symbol} & \colhead{Description}
}
\startdata
$i$ & index specifying a pixel\\
$\lambda_i$ & wavelength corresponding to a given pixel $i$\\
$\vg$ & fundamental stellar parameters, $T_{\rm eff}, \log(g), \Z, \A$\\
  & that parameterize a synthetic spectrum from the grid\\
$\vpp$ & stellar parameters $v \sin i$, $v_z$, $A_V$, and $R^2/d^2$ that\\
  & are applied during ``post processing'' of the synthetic spectrum\\
$\vtstar$ & $\{\vg,\vpp \}$\\
$\finst(\lambda)$ & data spectrum\\
$\fsynth(\lambda)$ & synthetic spectrum\\
$\vtcheb$ & the set of Chebyshev polynomial coefficients $\{c_0, c_1, \ldots, c_N\}$\\
$\vtline{1}$ & \\
$\vtlines$ & \\
$\vtorder{1}$ & \\
$\vtorders$ & \\
$\vt$ & the parameters $\{\vg, \vpp, \vN\}$ that completely describe a model spectrum\\
$\fDi$ & data flux for a given pixel, $D(\lambda_i)$\\
$\fD$ & data vector comprised of all $\fDi$, $i = \{1, \ldots, N\}$\\
$\fMi$ & model flux for a given pixel, $M(\lambda_i | \vt)$\\
$\fM$ & model vector comprised of all $\fMi$, $i = \{1, \ldots, N\}$\\
$\sigma_i$ & Poisson noise for a given pixel $i$\\
$R_i$ & residuals $\fDi - \fMi$\\
$\fR$ & residual vector $\fD - \fM$\\
$C$ & covariance matrix\\
$\sigma_{ij}$ & element in the covariance matrix\\
$r(\lambda_i, \lambda_j)$ & radial distance in wavelength space corresponding to $\Delta v$\\
$k_{\rm global}$ & global covariance kernel\\
$k_{\rm line}$ & regional covariance kernel\\
\enddata
\end{deluxetable}

\begin{deluxetable}{llrlr@{$\pm$}lr@{$\pm$}lr@{$\pm$}ll} 
\tablecaption{\label{table:tests} Tests}
\tablehead{
  \colhead{Object} & \colhead{Orders} & \colhead{$\lambda$ range [\AA]} & \colhead{library} &
  \multicolumn{2}{c}{$T_{\rm eff} \pm \sigma$} & \multicolumn{2}{c}{$\log g \pm \sigma$} &
  \multicolumn{2}{c}{$\Z \pm \sigma$} & \colhead{comments}
}
\startdata
WASP-14 & 22-24 & 5060-5315 & Kurucz &  &  &  &  &  & & No covariance\\
WASP-14 & 22-24 & 5060-5315& Kurucz & 6314 & 50 & 3.92 & 0.08 & -0.39 & 0.03 & Matern only\\
WASP-14 & 22-24 & 5060-5315& Kurucz & 6512 & 32 & \multicolumn{2}{c}{\nodata} & -0.27 & 0.02 & Matern + fixed $\log g = 4.29$\\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & & & & & & & No covariance \\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & & & & & & & Matern only \\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & & & \multicolumn{2}{c}{\nodata} & & & Matern + fixed $\log g = 4.29$ \\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & & & & & & & Regions included \\
\enddata
\end{deluxetable}
